%-------------------------
% Resume in Latex
% Based off of: https://www.overleaf.com/latex/templates/tech-engineer-resume-template/ydjtqpvcybkr
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{0.8in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{0.8in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\normalsize
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{6pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small#1} & \small#2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\vspace{1pt}\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\huge \scshape João Gabriel Ulian} \\ \vspace{1pt}
    \small \textit{Software Engineer} \\
    \href{mailto:joaogabrielulian@gmail.com}{\underline{joaogabrielulian@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/joaoulian}{\underline{https://www.linkedin.com/in/joaoulian}} $|$
    \href{https://github.com/joaoulian}{\underline{https://github.com/joaoulian}}
\end{center}

%-----------SUMMARY-----------
\section*{Summary}
\vspace{4pt}
\small{Versatile software engineer focusing on well-designed backend services. Extensive experience with NodeJS (Typescript) in different business contexts like Health, and SaS. Passionate about software architecture patterns like solid, clean architecture, and DDD.}

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
\vspace{4pt}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \footnotesize{\item{
     \textbf{Languages}{: Javascript, Typescript, SQL} \\
     \textbf{Frameworks}{: ReactJS, GraphQL} \\
     \textbf{Databases}{: Postgres, MySQL, MongoDB, Firestore, Kafka} \\
     \textbf{Other}{: DDD and Clean Arch, Microservices, Event-based architecture}
    }}
 \end{itemize}


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Software Engineer at \href{https://practice.do}{Practice}}{Jul 2023 -- Now}
      {Stack: Typescript, OpenAPI, GCP, Firestore, OpenFGA, NextJS, Tailwind, Zapier, Stripe}      {Montreal, Canada (Remote)}
      \resumeItemListStart
        \resumeItem{Developed APIs using NodeJS with Typescript and OpenAPI, persisting data on Firestore and handling events with GCP PubSub.}
        \resumeItem{Created a payment system integrating with Stripe.}
        \resumeItem{Created triggers and actions on Zapier.}
        \resumeItem{Worked on frontends using NextJS and TailwindCSS.}
    \resumeItemListEnd

    \resumeSubheading
      {Software Engineer at \href{https://zealous.app/}{Zealous}}{Oct 2022 -- Apr 2023}
      {Stack: Typescript, Postgres, GCP, NestJS, NextJS, GraphQL, Web3, Audio processing, ChatGPT}{Denver, USA (Remote)}
      \resumeItemListStart
        \resumeItem{Developed APIs using NodeJS with Typescript over NestJS, persisting data on Postgres and exposing it through GraphQL.}
        \resumeItem{Created a role-based access control integrating with Web3 and social medias}
        \resumeItem{Created a podcast processor that generates transcriptions and different insights based on the podcast, integrating with LLMs and using audio processing algorithms.}
      \resumeItemListEnd

      \resumeSubheading
      {Software Engineer at \href{https://www.octaneai.com/}{Octane AI}}{April 2022 -- Sept 2022}
      {Stack: Python, Flask, Redis, ReactJS, Shopify}{San Francisco, USA (Remote)}
      \resumeItemListStart
        \resumeItem{Developed APIs using Python with Flask, integrating with Shopify.}
        \resumeItem{Worked on dashboards using ReactJS.}
      \resumeItemListEnd   

      \resumeSubheading
      {Software Engineer at \href{https://alice.com.br/}{Alice}}{Dec 2021 -- April 2022}
      {Stack: Kotlin, Kafka, Postgres, FHIR, VueJS}{São Paulo, Brazil}
      \resumeItemListStart
        \resumeItem{Developed APIs in the context of interoperability between health institutions using technologies like Kotlin with microservices, Kafka, and FHIR protocol.}
        \resumeItem{Worked on some frontends using VueJS.}
      \resumeItemListEnd     
      
      \resumeSubheading
      {Technical Lead at Cuidas}{Jul 2021 -- Dec 2021}
      {Stack: NodeJS, Typescript, NextJS, GraphQL, MongoDB, AWS, DDD, Clean Arch}{São Paulo, Brazil}
      \resumeItemListStart
        \resumeItem{Designed solutions for user journey in the system before starts patient: begin lead and ends buyer}        
        \resumeItem{Coordinated team in discovery, development, and delivery process using SCRUM guideline}        
        \resumeItem{Documented architecture and design guidelines for rest of the company}   
      \resumeItemListEnd 
        
       \resumeSubheading
      {Software Engineer at Cuidas}{Jul 2019 -- Jul 2021}
      {Stack: NodeJS, Typescript, NextJS, GraphQL, MongoDB, AWS, DDD, Clean Arch}{São Paulo, Brazil}
      \resumeItemListStart
        \resumeItem{Early employee (one of three first software engineers)}     
        \resumeItem{Developed APIs using NodeJS with Typescript, exposing through GraphQL, persisting data on MongoDB, using DDD with Clean Architecture. I also created some lambda functions.}  
        \resumeItem{Developed Electronic Health Record from scratch in the context of Primary Care.}
      \resumeItemListEnd       
      
      \resumeSubheading
      {Software Engineer Intern at Embraer}{Mar 2017 -- Jul 2019}
     {Stack: Python, SAP, Excel, AngularJS, NodeJS}{São José dos Campos, São Paulo, Brazil}
      \resumeItemListStart
        \resumeItem{Structured and developed system for extracting and consolidating Quality Non-Conformities using Python integrated with SAP and Excel tables}
        \resumeItem{Developed dashboards using AngularJS, NodeJS, and MySQL.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
% \section{Projects}
%    \resumeSubHeadingListStart
%      \resumeProjectHeading
%          {\textbf{Gitlytics} $|$ \emph{Python, Flask, React, PostgreSQL, Docker}}{June 2020 -- Present}
%          \resumeItemListStart
%            \resumeItem{Developed a full-stack web application using with Flask serving a REST API with React as the frontend}
%            \resumeItem{Implemented GitHub OAuth to get data from user’s repositories}
%            \resumeItem{Visualized GitHub data to show collaboration}
%            \resumeItem{Used Celery and Redis for asynchronous tasks}
%          \resumeItemListEnd
%      \resumeProjectHeading
%          {\textbf{Simple Paintball} $|$ \emph{Spigot API, Java, Maven, TravisCI, Git}}{May 2018 -- May 2020}
%          \resumeItemListStart
%            \resumeItem{Developed a Minecraft server plugin to entertain kids during free time for a previous job}
%            \resumeItem{Published plugin to websites gaining 2K+ downloads and an average 4.5/5-star review}
%            \resumeItem{Implemented continuous delivery using TravisCI to build the plugin upon new a release}
%            \resumeItem{Collaborated with Minecraft server administrators to suggest features and get feedback about the plugin}
%          \resumeItemListEnd
%    \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Federal University of São Paulo (UNIFESP)}{São José dos Campos, São Paulo, Brazil}
      {Bachelor of Science: Computer Engineering}{2014 - 2019}
      \resumeItemListStart
        \resumeItem{Junior research in the field of mathematical modeling in the context of crisis management}
        \resumeItem{Junior research in the field of biomedical signal processing}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
